Response to Pachter's Review

### 2020-01-23 index.tex
one more figure
revision

So it is clear that Pachter's analysis was some sort of magic trick,
potentially a thought experiment, and a fraudulent one. It is highly
unlikely that a tenured and respected expert in computation and
statistics did not know the above result, expecially when a student he
suggests take an introductory statistics course immediately spotted it.
We claim and assert that he purposefully chose his 36 cutoff to try to
undermine our results.

>>>>

Perhaps removing Lior was a confounder. So we remove the top five
mathematicians from C.

\includegraphics{index_files/figure-latex/unnamed-chunk-45-1.pdf}

So it is clear that Pachter's analysis was some sort of magic trick,
potentially a thought experiment, and a misleading one. It is highly
unlikely that a tenured and respected expert in computation and
statistics did not know the above result, expecially when a student he
suggests take an introductory statistics course immediately spotted it.
We claim and assert that he purposefully chose his 36 cutoff to try to
undermine our results.
